A Large-Scale Study of the Use of Eval in R

### 2020-08-22 inst/paper/main.tex
Degree of polymorphism

@@

>>>>

\graphicspath{{img/}}

@@

We look at how \emph{polymorphic} the \c{expr} argument of \eval can be, \emph{i.e.} how many different types of the resolved \c{expr} there are per call sites, in Figure~\ref{fig:polymorphism}. 89\% of the call sites are \emph{monomorphic}.

\begin{figure}
    \includegraphics[width=\columnwidth]{polymorphism-1}
    \caption{Degree of polymorphism of \c{expr} per call sites.} \label{fig:polymorphism}
\end{figure}
